\documentclass[a4paper,14pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}


\setlength{\parindent}{0pt}


\begin{document}
    %\maketitle
    {\LARGE\bf\begin{center}
        Society Charter\\
        {\today}
    \end{center}}

    \section*{Article 1: Name of society}
    \subsection*{Section A}
    Makerere University Photonics Society (MUPhS)

    \section*{Article 2: Society Purpose}
    \subsection*{Section A}%purpose and objective of the club
    To provide a forum for students interested in photonics and related fields to learn, network and engage with each other and professionals in the field.
    Students interested in fields such as nuclear energy, optical fibre, lasers, quantum,solar, biosensors only to mention but a few.
    \subsection*{Section B}%hoped to be accomplished
    We hope to achieve this by,
    \begin{enumerate}
        \item Organising events such as workshops, webinars, seminar and paper contests to increase knowledge in photonics.
        \item Establish and maintain relationships with professionals in the optics industry to provide opportunities for students to learn and engage with students in the field.
        \item Encourage and support student participatoin in optics research and development projects.
        \item Establish a mentorship program to provide guidance and support for students interested in persuing careers in optics.
        \item Facilitate networking and collaboration among studentsand professionals in the field.
    \end{enumerate}
    \subsection*{Section C}%how does community benefit
    By pursuing these activities we hope to create a vibrant and active community of students interested in optics and to provide them with resources and support where possibly can so that they succed in their careers. \\
    We aim at working together and leveraging the expertise and resources of our members and partners so as to make a meaningful contribution to photonics.

    \section*{Article 3: Membership}
    \subsection*{Section A}
    Only Makerere University students can be members irrespective of the field of study.\\
    Only active members vote and hold office.\\
    Membership subscription renews annual at 10USD but free for first year.\\

    \section*{Article 4: Officers/Elections}
    \subsection*{Section A}
    There shall be five student officers, the President, Vice President, Treasurer, Secretary, Webmaster advised by a faculty member.
    \subsection*{Section B}
    \begin{enumerate}
        \item Advisor: Provide guidance in all activities and organisation of the society. May appoint or dismiss leaders.
        \item President: Serves as official representative of the club. Convenes and chairs society meetings. Sets club meetings agendas. May propose and vote on all club matters.
        \item Vice President: Assists club president with all club matters. May propose and vote on all club matters.
        \item Treasurer: Handles all financial society matters. May propose and vote on all club matters.
        \item Secretary: Records and distributes the minutes of all club meetings. May propose and vote on all club matters.
        \item Webmaster: Updates the society social media handles and website.May propose and vote on all club matters.
    \end{enumerate}
    \subsection*{Section C}
    Voting prpocess will takeplace on IEEE vtools evoting.
    Voting will take place at the start of a new academic year in August/September
    Officers are eligible to stay in power for a maximum of two terms
    A handover session is to be held to delegate new leaders.

    \section*{Article 5: Meetings}
    \subsection*{Section A} Meetings will be held twice a month on Thursday afternoons.
    \subsection*{Section B} Special meetings will be held In case of an event or a proposal and mode of communication will be IEEE enotice and WhatsApp.
    \subsection*{Section C} Meetings must contain atleast 51 percent attendance of the cabinet members and budget approvals require all six excecutives.

    \section*{Article 6: Charter Ammendments}
    \subsection*{Section A}
    An ammendment may be initiated by any member of the club and approved by 2/3 of the available members at a meeting.
    \subsection*{Section B}
    All ammendments made will be shared to members via email through IEEE e-notice.\\ The president will share a copy of the changed charter to the students guild.

    \begin{center}
        {\LARGE\em\bf END}
    \end{center}

\end{document}
